Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-01 latex/robdml.tex
tex

\textbf{Deep Metric Learning.}
%
A wide range of application problem such as image retrieval~\cite{imagesim2},
cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
can be formularized as a deep metric learning problem.
%
Deep metric learning has been found vulnerable to adversarial attacks as
well~\cite{advrank,advorder}, which will result in undesired
implications on safety, security, or fairness of a deep metric learning
application.
%
In contrast, the defense methods for enhancing the adversarial robustness of deep
metric learning are less explored.
%
Mo \etal~\cite{advrank} present an adversarial training method with adversarial
examples maximizing the embedding move distance off its original location.
%
Anti-Collapse Triplet defense~\cite{robrank} forces the model
to separate collapsed positive and negative samples in order to learn
robust features.
%
However, the existing defense methods refrain from adopting Madry's min-max
adversarial training paradigm due to the model being too easy to collapse
with excessively hard adversarial samples.

>>>>

\textbf{Deep Metric Learning.}
%
A wide range of application problem such as image retrieval~\cite{imagesim2},
cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
can be formularized as a deep metric learning problem.
%
Deep metric learning has been found vulnerable to adversarial attacks as
well~\cite{advrank,advorder}, which will result in undesired
implications on safety, security, or fairness of a deep metric learning
application.
%
In contrast, the defense methods for enhancing the adversarial robustness of deep
metric learning are less explored.
%
Zhou \etal~\cite{advrank} present an adversarial training method with adversarial
examples maximizing the embedding move distance off its original location.
%
Anti-Collapse Triplet~\cite{robrank} forces the model
to separate collapsed positive and negative samples in order to learn
robust features.
%
However, the existing defense methods refrain from adopting Madry's min-max
adversarial training paradigm due to the model being too easy to collapse
with excessively hard adversarial samples.
